
          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%

\section{Summary}
\setcounter{theorem}{0}
\setcounter{equation}{0}

%\cite{vanDerVaart1996}
%\cite{Kosorok2008}

%\renewcommand{\theenumi}{\alph{enumi}}
%\renewcommand{\labelenumi}{\textnormal{(\theenumi)}$\;\;$}
\renewcommand{\theenumi}{\roman{enumi}}
\renewcommand{\labelenumi}{\textnormal{(\theenumi)}$\;\;$}

          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%

%$\mathfrak{A}$, $\mathscr{F}$ $\mathcal{F}$
In an abelian category, the following statements are true:
\begin{itemize}
\item
	A zero object exists.
	Kernels and cokernels of morphisms exist.
	Hence, short exact sequences make sense.
\item
	The Snake Lemma holds, which in turn implies that
	short exact sequences of cochain complexes generate long exact sequences in cohomology.
\item
	When the abelian category is the category of abelian groups or $R$-modules,
	the construction of the connecting homomorphisms involves a simple diagram chase.
	For an arbitrary abelian category, that construction involves either the deep result
	of Mitchell's Embedding Theorem, or clever but hard-to-motivate tricks.
\item
	However, when the abelian category has enough injectives,
	the construction of the connecting homomorphisms is formally identical to
	that for $R$-modules. 
\item
	Let $(X,\mathcal{O}_{X})$ be a ringed space.
	Then, the category of sheaves of $\mathcal{O}_{X}$-modules
	is an abelian category with enough injectives, and
	the global section functor $\Gamma_{X}$ is a left-exact functor.
	The $p^{\textnormal{th}}$ right derived functor
	\begin{equation*}
	R^{p}\Gamma_{X}
	\;\; : \;\;
	\left(\begin{array}{c} \textnormal{abelian category of} \\ \textnormal{sheaves of $\mathcal{O}_{X}$-modules} \end{array}\right)
	\;\;\longrightarrow\;\;
	\left(\begin{array}{c} \textnormal{abelian category of} \\ \textnormal{abelian groups} \end{array}\right)
	\end{equation*}
	is thus well-defined.
	The $p^{\textnormal{th}}$ sheaf cohomology functor $H^{p}(X,\,\cdot\,)$ is defined to be:
	\begin{equation*}
	H^{p}(X,\,\cdot\,)
	\;\; := \;\;
		R^{p}\Gamma_{X}(\,\cdot\,)
	\end{equation*}
\item
	Let $(X,\mathcal{O}_{X})$ be a scheme (respectively, complex analytic space).
	The category of \textit{coherent algebraic sheaves} (respectively, \textit{coherent analytic sheaves})
	is an abelian category, and it is a full subcategory of the category of sheaves of $\mathcal{O}_{X}$-modules.
\item
	Let $(X,\mathcal{O}_{X})$ be a scheme.
	Let $\mathcal{F}$ be an arbitrary coherent or quasi-coherent sheaf of $\mathcal{O}_{X}$-modules,
	and $H^{p}(X,\mathcal{F})$ its $p^{\textnormal{th}}$ sheaf cohomology.
	The large body of results about $H^{p}(X,\mathcal{F})$ forms the core foundational results of modern algebraic geometry.
\end{itemize}

          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%
